Asymmetric Agents and their Willingness to Fight\\ Customer Loyalty and its Impact on Competition

### 2015-10-20 Paper1.tex
added loyalty example

>>>>

\subsection{Loyalty}
No consider the case of both firms having a loyal customer base such that $g'(\theta)>0$ to the right of the center. Firm $2$ is the disadvantaged firm, with $x_2<x_1$. This can be due to a difference in costs or value extraction. The reaction function is:

\begin{align}
\frac{\d x_1}{\d x_2} &= A_i^{-1} \underbrace{\left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}\right.}_{>0} - \left.g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{1}{c_1}
\end{align}
Thus, the sign of the reaction of firm $1$ depends on the relative expression of the changes in competition. If the intensity of competition increases significantly in response to a reduction of firm $2$'s efforts, firm $1$ will raise its efforts. Similarly, if the value extraction is fixed, an increase in the efforts of firm $1$ will raise firm $2$'s incentive to exert efforts. Paradoxically, supporting the market leader raises the efforts of the laggard, and raising the efforts of the laggards, reduces the efforts of the market leader. This is precisely the opposite of what we expect.

This effect is affected by the changes to the value extraction. In general the firm that gains an advantage has a higher incentives to raise its efforts and the losing firm gains incentives to lower its efforts. This can partially offset the result in the previous paragraph.
